\plaintitle

### 2016-09-21 drafts/labor/relationships.tex
looked through complexity
relationships crowd perspective

\subsubsection{\crowdworkpers}
\topic{The relationships of workers
% with their work,
with their peers and
with requesters
are nuanced and not especially well--understood.}
Researchers have begun to appreciate
the sociality of crowd workers in labor markets;
still, the study of these communities is made more challenging by
the limited access to workers on these sites of work
inherent to digital spaces made without social affordances
\cite{crowdcollab,miller2011understanding}.
We can break this general body of work into two subgroups:
workers' relationships
\begin{inlinelist}
% \item with \textit{work}, % \nameref{ch:workRelationship},
\item with \textit{requesters}, and
\item with \textit{other workers}.
\end{inlinelist}
We'll look at workers' relationships with work itself, which we'll discover
gives us insight into why people engage in crowd work in the first place.

\topic{\ali{some topic sentence that brings together the debate where
one side blames Turkers for being bad at Turking and
another side blames requesters for not understanding Turkers as a culture of people.}}
Some research frames this tension as the Turker's problem
(see, for example, \citeauthor{MaliciousCrowdworkersGadiraju}'s work,
which frames the problem of unpredictable work as the result of ``malicious'' crowd workers),
\cite{MaliciousCrowdworkersGadiraju,Sheng:2008:GLI:1401890.1401965,Ipeirotis:2010:QMA:1837885.1837906}.

Early on, \citeauthor{turkopticon} highlighted
the information asymmetry between workers and requesters on AMT,
leading to the creation of \TO, a site which allows
Turkers to rate and review requesters
\cite{turkopticon}.
\citeauthor{dynamo} took this critique on information asymmetry and power imbalances a step further,
designing \DO~to facilitate
Turkers acting collectively to bring about changes to their circumstances
--- this led to the Academic Requester Guidelines
\cite{dynamo}.
This unbridled power that requesters have over workers and
the resultant stress and frustration that this generates
has been part of the undercurrent of research into
the tense relationships between workers and requesters
\cite{fixingChaos,dynamo}.

\topic{The frustration that workers experience dealing with requesters
seems to precipitate frustration and mistrust between crowd workers, as well.}
\citeauthor{dynamo} describes ``mega--drama'' among workers on forums for Turkers;
\citeauthor{irani2015cultural} and \citeauthor{storiesIraniSilberman} discuss
the culture of crowd work and the study thereof.
\citeauthor{crowdcollab} quantifies and maps this social network of Turkers.
\citeauthor{takingAHITMcInnis} takes these observations and considers
what a crowd work platform might look like if it were to be designed more inclusively
\cite{dynamo,irani2015cultural,storiesIraniSilberman,crowdcollab,takingAHITMcInnis}.
The overarching theme of the research in this space has been
documenting the struggle of crowd workers
and attempting to intervene in constructive ways, while walking the balancing act
(especially in the cases of \citeauthor{irani2015cultural} and later \citeauthor{storiesIraniSilberman})
as we think about the culture of crowd workers.

@@

\onlyinsubfile{
\printbibliography
}
\end{document}

>>>>

HCI and CSCW have largely framed themselves around supporting work rather than becoming an infrastructural layer enabling it. While all artifacts have politics, this shift into computational labor systems has directly impacted the lives and livelihood of workers. So, it is important to understand: what will the future look like for the workers who use these systems?

\subsubsection{\crowdworkpers}
\begin{comment}
	- Workers do it for money
	- Workers coordinate and communicate (gray, being a turker, team stuff). there is mega-drama
	- Workers don't like requesters. have tried to organize
\end{comment}

One of the initial questions that researchers asked was, who are the crowd workers and what draws them to crowd work?
Early literature emphasized motivations like fun and spare change, but this narrative soon shifted to emphasize that many workers use platforms such as Amazon Mechanical Turk as a primary source of income~\cite{kaufmann2011more,ipeirotis2010demographics,Antin2012a}.
Despite this, Mechanical Turk is a low-wage affair for most workers in the United States~\cite{ipeirotis2010demographics,martin2014being,gupta2014turk}.
Thus, those who choose to opt out of the traditional labor force and spend significant time on Mechanical Turk are especially motivated by the opportunity for autonomy and skill variety~\cite{kaufmann2011more}.
Due to valuing autonomy, it is tempting to ascribe attitudes of ``pity the workers'' to Turkers, but this frame is increasingly rejected by workers and designers as patronizing~\cite{storiesIraniSilberman}.

% \topic{The relationships of workers
% % with their work,
% with their peers and
% with requesters
% are nuanced and not especially well--understood.}
% We can break this general body of work into two subgroups:
% workers' relationships
% \begin{inlinelist}
% % \item with \textit{work}, % \nameref{ch:workRelationship},
% \item with \textit{requesters}, and
% \item with \textit{other workers}.
% \end{inlinelist}
% We'll look at workers' relationships with work itself, which we'll discover
% gives us insight into why people engage in crowd work in the first place.

Workers' relationships with requesters are fraught.
% \topic{\ali{some topic sentence that brings together the debate where
% one side blames Turkers for being bad at Turking and
% another side blames requesters for not understanding Turkers as a culture of people.}}
Workers are often blamed for any low-quality work, regardless of whether they are responsible~\cite{martin2014being,takingAHITMcInnis}.
Some research is extremely open about this position, blaming unpredictable work on ``malicious'' workers~\cite{MaliciousCrowdworkersGadiraju} or those with ``a lack of expertise, dedication [or] interest''~\cite{Sheng:2008:GLI:1401890.1401965}.
% (see, for example, \citeauthor{MaliciousCrowdworkersGadiraju}'s work,
% which frames the problem of unpredictable work as the result of ``malicious'' crowd workers),
% \cite{MaliciousCrowdworkersGadiraju,Sheng:2008:GLI:1401890.1401965,Ipeirotis:2010:QMA:1837885.1837906}.
Workers resent this position --- for good reason.
\citeauthor{turkopticon} highlighted the information asymmetry between workers and requesters on AMT, leading to the creation of \TO, a site which allows Turkers to rate and review requesters~\cite{turkopticon}.
Dynamo then took this critique on information asymmetry and power imbalances a step further, designing a platform to facilitate
Turkers acting collectively to bring about changes to their circumstances~\cite{dynamo}.
This unbridled power that requesters have over workers and
the resultant stress and frustration that this generates
has been part of the undercurrent of research into
the tense relationships between workers and requesters
\cite{fixingChaos,dynamo}.

Researchers have also begun to appreciate the sociality of crowd workers.
Because the platforms do not typically include social spaces, workers instead congregate off-platform in forums and mailing lists.
There, Turkers exchange advice on high-paying work, talk about their earnings, build social connections, and discuss requesters~\cite{martin2014being}.
Many crowd workers know each other through offline and online connections, coordinating behind-the-scenes despite the platforms encouraging independent work~\cite{crowdcollab,yin2016communication}.
However, the frustration and mistrust that workers experience with requesters does occasionally boil over on the forums. 
This behavior has come to be known as ``mega--drama'' amongst such workers~\cite{dynamo}.
Still, the study of these communities is made challenging because most of these platforms do not themselves include social affordances for workers~\cite{miller2011understanding}.

% \topic{The frustration that workers experience dealing with requesters
% seems to precipitate frustration and mistrust between crowd workers, as well.}
% \citeauthor{dynamo} describes ``mega--drama'' among workers on forums for Turkers;
% \citeauthor{irani2015cultural} and \citeauthor{storiesIraniSilberman} discuss
% the culture of crowd work and the study thereof.
% \citeauthor{crowdcollab} quantifies and maps this social network of Turkers.
% \citeauthor{takingAHITMcInnis} takes these observations and considers
% what a crowd work platform might look like if it were to be designed more inclusively
% \cite{dynamo,irani2015cultural,storiesIraniSilberman,crowdcollab,takingAHITMcInnis}.
% The overarching theme of the research in this space has been
% documenting the struggle of crowd workers
% and attempting to intervene in constructive ways, while walking the balancing act
% (especially in the cases of \citeauthor{irani2015cultural} and later \citeauthor{storiesIraniSilberman})
% as we think about the culture of crowd workers.

@@

% \onlyinsubfile{
% \balance{}
% \printbibliography
% }
\end{document}
